Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-01 writing/DraftExposurePaper/DraftExposurePaper.Rmd
work on good/bad list

Good Characteristics:
- Flooding-- Most associated with death; property damage
- Precipitation
- Wind (potentially weighted)

Bad Characteristics:
- Distance alone
- Wind alone

>>>>

Good Characteristics:
- Measureable at the county/sub-county level
- Internally consistant (either within a study or for a particular storm)
+ Takes into account the unique characteristics of a particular storm and county's location in assessing exposure
- Flooding-- Most associated with death; property damage
- Precipitation
+ Gauge data if available
- Wind (potentially weighted based on relation to the storm track), though wind alone has proven not to be sufficient in identifying the most affected region in some cases (e.g., Hurricane Andrew in 1992)[@Fronstin1994]. Therefore wind alone is not sufficient in all cases (as is commonly done using the Staffir-Simpson scale).

Bad Characteristics:
- Distance alone
- Wind alone
- Metrics that cannot be widely measured at the county or sub-county level (i.e., stress)
